### 2023-01-31 manuscript.tex
Some citations [ci skip]
This build is based on
https://github.com/stain/2022-fdo-paper/commit/91171dc6c031928ebbaa06767feaef4bcede30f4.

This commit was created by the following CI build and job:
https://github.com/stain/2022-fdo-paper/commit/91171dc6c031928ebbaa06767feaef4bcede30f4/checks
https://github.com/stain/2022-fdo-paper/actions/runs/4055611488

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/c0dc59e999a0bc215e5d5e0509a2cf6927bcbba4/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/c0dc59e999a0bc215e5d5e0509a2cf6927bcbba4}{stain/2022-fdo-paper@c0dc59e}
on January 31, 2023.

>>>>

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/91171dc6c031928ebbaa06767feaef4bcede30f4/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/91171dc6c031928ebbaa06767feaef4bcede30f4}{stain/2022-fdo-paper@91171dc}
on January 31, 2023.
